\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-04 ms.tex
orbits

% \title{A young star cluster in the Galactic halo: \\
% Recent star formation associated with the Leading Arm of the Magellanic stream}
\title{\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\
       a recent star formation event in the leading arm of the Magellanic stream}}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{orbits.pdf}
\caption{TODO:}
\label{fig:orbits}
\end{figure}

>>>>

% \title{A young star cluster in the Galactic halo: \\
% Recent star formation associated with the Leading Arm of the Magellanic stream}
\title{\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\
       a recent star formation event in the leading arm of the Magellanic stream?}}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/orbits.pdf}
\caption{TODO:}
\label{fig:orbits}
\end{figure}
